---
title: "hw_6"
author:
  - Alejandra Pedraza
  - W. Jamie Yang
format: pdf
editor: visual
execute:
  eval: true
  echo: false
fig-width: 6.5
fig-height: 8
bibliography: references.bib
link-citations: true
embed-resources: true 
---

```{r}
#| label: loading libraries 
#| include: false

library(tidyverse)
library(rio)
library(here)
```

```{r}
#| label: loading data 

star <- import(here("data", "star.csv")) %>%
  as_tibble()

```

# Literature Review

Bonilla-Silva argues that the United States' racial system is transitioning into a tri-racial system comprised of whites, "honorary white", and Blacks, and that phenotype will be the key determinant in dictating where one falls [@bonilla-silva2018].

In outlining the tenets of Black Feminist Thought, Patricia Hill collins argues that portrayals of African-American women as mammies, matriarchs, welfare recipients, and hot mommas help justify Black women's oppression [@collins2009].

Yosso argues that a Critical Race Theory (CRT) lens is useful to transition away from subtractive teaching practices and recognize that communities of color nurture community cultural wealth through at least 6 forms of capital--aspirational, navigational, social, linguistic, familial and resistance capital [@yosso2005].

Mora argues that the insitutionalization of panethnic Hispanic identity evolved through processes of 1) co-optation through state classification, 2) negotiation, and 3) marketing by activists, government officials, and media executives [@mora2014].

\newpage

# References
