---
title: "hw_6"
author:
  - Alejandra Pedraza
  - W. Jamie Yang
format: pdf
editor: visual
execute:
  eval: true
  echo: false
fig-width: 6.5
fig-height: 8
bibliography: references.bib
link-citations: true
embed-resources: true 
---

# Commit 1 

```{r}
#| label: loading libraries 
#| include: false

library(tidyverse)
library(rio)
library(here)
library(dplyr)
library(knitr)
library(ggplot2)

```

```{r}
#| label: loading data 

star <- import(here("data", "star.csv")) %>%
  as_tibble() %>%
  mutate(recode(frl, 
         yes = "Free/Reduced Price Meals",
         No = "Paid Meals"))

view(star)

```

# Commit 2: Literature Review

Bonilla-Silva argues that the United States' racial system is transitioning into a tri-racial system comprised of whites, "honorary white", and Blacks, and that phenotype will be the key determinant in dictating where one falls [@bonilla-silva2018].

In outlining the tenets of Black Feminist Thought, Patricia Hill collins argues that portrayals of African-American women as mammies, matriarchs, welfare recipients, and hot mommas help justify Black women's oppression [@collins2009].

Yosso argues that a Critical Race Theory (CRT) lens is useful to transition away from subtractive teaching practices and recognize that communities of color nurture community cultural wealth through at least 6 forms of capital--aspirational, navigational, social, linguistic, familial and resistance capital [@yosso2005].

Mora argues that the insitutionalization of panethnic Hispanic identity evolved through processes of 1) co-optation through state classification, 2) negotiation, and 3) marketing by activists, government officials, and media executives [@mora2014].

# Commit 3

```{r}
#| label: data wrangling
star1 <- star %>%
  group_by(sex, frl) %>% 
  mutate(math_mean = mean(tmathss),
         math_sd = sd(tmathss), 
         rdg_mean = mean(treadss),
         rdg_sd = sd(treadss))  %>%
  select(sex, frl, math_mean, math_sd, rdg_mean, rdg_sd) 

view(star1)
```
  
```{r}
#| label: make a table 
star1 %>% 
  summarize(across(c(math_mean, math_sd, rdg_mean, rdg_sd), ~mean(., na.rm =TRUE))) %>%
  kable(col.names = c("sex", "frl", "math_mean", "math_sd", "rdg_mean", "rdg_sd"),
        digits = 2,
        booktabs = TRUE) 
```

# Commit 4

```{r}
#| label: make a plot
star %>% 
  ggplot(aes(x = totexp, y = tmathss)) +
  geom_point(size = 0.5, color = "gray70") +
  geom_smooth(method = lm, se = TRUE, aes(color = frl)) +
  labs(
    title = "Relation between teacher experience and math scores",
    subtitle = "Separate regression lines displayed by free/reduced price lunch status",
    x = "Teacher Experience (years)",
    y = "Total Math Scale Score",
    color = "frl"
  ) +
  theme_minimal() +
  theme(legend.position = "bottom") 
  

  # scale_fill_discrete(name = "Lunch status", 
                      #labels = c("Free/Reduced Price Meals", "Paid Meals"))
   

```

I successfully positioned the legend at the bottom but couldn't figure out how to change the legend title and the texts. 

\newpage

# References









